The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
grammar for sentence defining drugs to be only recognised as such within a specified context
add FIXME note for a possibly ambiguous sentence
an authoritative
in particular, there are multiple DOI authoritative sources, so an is more correct and easier to read

It should also be noted that all drug-like entities in ChEMBL are not ontologically
subclassing a drug class. Instead, we give the entities the role of drug: only within a
particular context, they would be drug. If not used as medication, they are not drug.
Moreover, the triples only attach this drug role to approved drugs, as defined by the
ChEMBL database. All drug-like entities in the database do not have the role of drug.
The role is triplified using the OBO and ChEBI ontologies in the following manner,
where CHEBI\_23888 is the ontological entry for ``drug role'' in ChEBI:

@@

The literature from which all this data was extracted, is replicated from the database,
but only a subset of the possible information about that literature is provided. In all cases 
the PubMed Identifiers (PMIDs) and Digital Object Identifiers (DOIs) are used to link
to authoritative database, as outlined later in this paper.
The properties are provided using the BIBO ontology, which is an open sourced ontology
for bibliographic information, compatible with the CiTO ontology:

>>>>

It should also be noted that all drug-like entities in ChEMBL are not ontologically
subclassing a drug class. Instead, we give the entities the role of drug, and only within a
particular context would they be a drug. If not used as medication, they are not a drug.
Moreover, the triples only attach this drug role to approved drugs, as defined by the
ChEMBL database. 
% FIXME: What does the following exactly mean? It isn't clear whether it actually means:
% Not all drug-like entities in the database have the role of drug
All drug-like entities in the database do not have the role of drug.
The role is triplified using the OBO and ChEBI ontologies in the following manner,
where CHEBI\_23888 is the ontological entry for ``drug role'' in ChEBI:

@@

The literature from which all this data was extracted, is replicated from the database,
but only a subset of the possible information about that literature is provided. In all cases 
the PubMed Identifiers (PMIDs) and Digital Object Identifiers (DOIs) are used to link
to an authoritative database, as outlined later in this paper.
The properties are provided using the BIBO ontology, which is an open sourced ontology
for bibliographic information, compatible with the CiTO ontology:
